Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2020-11-19 paper/main.tex
update paper

  \caption{Mean fitness (and standard deviation) of the best solution found at the end of each run, over 10 independent runs for each problem instance. The 95\% confidence interval corresponds to the two independent samples t-test on the mean difference between the fitness of UMM minus the one of CEGO. Mean runtime is shown in hours. CEGO runs were stopped after 144 hours. This was the case for all LOP instances.\label{tab:results}}

@@

An interesting result is that the behavior of UMM (and the same for CEGO) on
the PFSP (and some QAP instances) is close to random. The same behavior is
observed for CEGO, which seems to have been never reported until now.
This result may be due to the distance
metric used, but further analysis is needed to corroborate this
conjecture. Here, we have focused on Kendall's-$\tau$ distance, however, we are certain it is
possible to extend UMM to other distance metrics, which will allow us to
dynamically select among various distance metrics for an unknown black-box
% \ekhine{}{estoy totalmente en contra de esto :) }
permutation landscape~\citep{ZaeStoBar2014:ppsn}. Also, as shown by our
experiments, the behavior of the parameters ($r_1$ and $r_2$) of UMM is not
always obvious, thus a more detailed analysis would be needed to provide either
generally good static values or an online adaptation approach. Finally, we have
used here three very different combinatorial problems (LOP, PFSP and QAP) as
black-box benchmarks. However, an even more diverse range of problems would be
needed to understand the behavior of UMM on real-world black-box combinatorial
landscapes.

@@

%% MANUEL: Blind, so no acknowledgments yet.
\begin{smaller}
  \paragraph*{Reproducibility.} Source code, datasets and scripts necessary to reproduce the results are available at \supplement.
  \vspace*{-1em}
\paragraph*{Acknowledgements.}
% M.\@ L\'opez-Ib\'a\~nez is a ``Beatriz Galindo'' Senior Distinguished Researcher (BEAGAL 18/00053) funded by the Ministry of Science and Innovation of the Spanish Government.
%
%\manuel{}{: We should also thank the COST ACTION: Ask Carlos?} \ekhine{}{Sure!, esto no habra q ponerlo aun por ser blind, no?}
Thanks to: Hao Wang (Leiden University) for pointing us to the arguments of
\citep{EriPeaGar2019scalable}; Thomas Stützle (Université libre de Bruxelles) for suggesting works
about differences between QAPLIB instances; and Ahmed Boujaada for the experimental support. 
\end{smaller}

>>>>

  \caption{Mean fitness (and standard deviation) of the best solution found. % at the end of each run, over 10 independent runs for each problem instance. The 95\% confidence interval corresponds to the two independent samples t-test on the mean difference between the fitness of UMM minus the one of CEGO. 
  Mean runtime is shown in hours. 
  %CEGO runs were stopped after 144 hours. This was the case for all LOP instances.
  \label{tab:results}}

@@

An interesting result is that the behavior of UMM (and the same for CEGO) on
the PFSP (and some QAP instances) is close to random. %The same behavior is
%observed for CEGO, which seems to have been never reported until now.
This result may be due to the distance
metric used, but further analysis is needed to corroborate this
conjecture. Here, we have focused on Kendall's-$\tau$ distance, however, we are certain it is
possible to extend UMM to other distance metrics, which will allow us to
dynamically select among various distance metrics for an unknown black-box
% \ekhine{}{estoy totalmente en contra de esto :) }
permutation landscape~\citep{ZaeStoBar2014:ppsn}. Also, as shown by our
experiments, the behavior of the parameters ($r_1$ and $r_2$) of UMM is not
always obvious, thus a more detailed analysis would be needed to provide either
generally good static values or an online adaptation approach. Finally, we have
used here three very different combinatorial problems (LOP, PFSP and QAP) as
black-box benchmarks. However, an even more diverse range of problems would be
needed to understand the behavior of UMM on real-world black-box combinatorial
landscapes.

@@

%% MANUEL: Blind, so no acknowledgments yet.
\begin{smaller}
  \paragraph*{Reproducibility.} Source code, datasets and scripts necessary to reproduce the results are available at \supplement.
  \vspace*{-1em}
\paragraph*{Acknowledgements.} Blind
% M.\@ L\'opez-Ib\'a\~nez is a ``Beatriz Galindo'' Senior Distinguished Researcher (BEAGAL 18/00053) funded by the Ministry of Science and Innovation of the Spanish Government.
%
%\manuel{}{: We should also thank the COST ACTION: Ask Carlos?} \ekhine{}{Sure!, esto no habra q ponerlo aun por ser blind, no?}
%Thanks to: Hao Wang (Leiden University) for pointing us to the arguments of
%\citep{EriPeaGar2019scalable}; Thomas Stützle (Université libre de Bruxelles) for suggesting works
%about differences between QAPLIB instances; and Ahmed Boujaada for the experimental support.

\end{smaller}
